---
title: "tidysl Cheat Sheet"
author: "tidysl Team"
date: today
format:
  html:
    toc: true
    toc-location: left
    theme: flatly
    code-fold: false
    df-print: paged
  pdf:
    toc: true
    number-sections: false
    colorlinks: true
execute:
  echo: true
  eval: false
---

## Core Functions

| Function | Description | Example |
|----------|-------------|---------|
| `tl_model()` | Fit a supervised learning model | `tl_model(data, medv ~ ., method = "linear")` |
| `predict()` | Generate predictions | `predict(model, new_data)` |
| `tl_evaluate()` | Evaluate model performance | `tl_evaluate(model, test_data)` |
| `tl_cv()` | Perform cross-validation | `tl_cv(data, formula, method, folds = 5)` |
| `summary()` | Show model summary | `summary(model)` |

## Model Types

| Method | Description | Usage |
|--------|-------------|-------|
| `"linear"` | Linear regression | `tl_model(data, y ~ x, method = "linear")` |
| `"polynomial"` | Polynomial regression | `tl_model(data, y ~ x, method = "polynomial", degree = 2)` |
| `"logistic"` | Logistic regression | `tl_model(data, factor_y ~ x, method = "logistic")` |
| `"ridge"` | Ridge regression | `tl_model(data, y ~ x, method = "ridge")` |
| `"lasso"` | Lasso regression | `tl_model(data, y ~ x, method = "lasso")` |
| `"elastic_net"` | Elastic Net | `tl_model(data, y ~ x, method = "elastic_net", alpha = 0.5)` |
| `"tree"` | Decision tree | `tl_model(data, y ~ x, method = "tree")` |
| `"forest"` | Random forest | `tl_model(data, y ~ x, method = "forest", ntree = 100)` |
| `"boost"` | Gradient boosting | `tl_model(data, y ~ x, method = "boost", n.trees = 100)` |
| `"svm"` | Support vector machine | `tl_model(data, y ~ x, method = "svm", kernel = "radial")` |
| `"nn"` | Neural network | `tl_model(data, y ~ x, method = "nn", size = 5)` |
| `"deep"` | Deep learning | `tl_model(data, y ~ x, method = "deep", hidden_layers = c(32, 16))` |

## Regression Visualization

| Function | Description | Example |
|----------|-------------|---------|
| `tl_plot_actual_predicted()` | Actual vs predicted values | `tl_plot_actual_predicted(model, test_data)` |
| `tl_plot_residuals()` | Residuals plot | `tl_plot_residuals(model, type = "fitted")` |
| `tl_plot_diagnostics()` | Regression diagnostics | `tl_plot_diagnostics(model)` |
| `tl_plot_intervals()` | Confidence/prediction intervals | `tl_plot_intervals(model, new_data)` |

## Classification Visualization

| Function | Description | Example |
|----------|-------------|---------|
| `tl_plot_roc()` | ROC curve | `tl_plot_roc(model, test_data)` |
| `tl_plot_confusion()` | Confusion matrix | `tl_plot_confusion(model, test_data)` |
| `tl_plot_calibration()` | Calibration curve | `tl_plot_calibration(model, test_data)` |
| `tl_plot_precision_recall()` | Precision-recall curve | `tl_plot_precision_recall(model, test_data)` |
| `tl_plot_lift()` | Lift chart | `tl_plot_lift(model, test_data)` |
| `tl_plot_gain()` | Gain chart | `tl_plot_gain(model, test_data)` |

## Model Interpretation

| Function | Description | Example |
|----------|-------------|---------|
| `tl_plot_importance()` | Feature importance | `tl_plot_importance(model, top_n = 10)` |
| `tl_plot_partial_dependence()` | Partial dependence plot | `tl_plot_partial_dependence(model, "variable")` |
| `tl_plot_tree()` | Decision tree visualization | `tl_plot_tree(model)` |
| `tl_plot_svm_boundary()` | SVM decision boundary | `tl_plot_svm_boundary(model, "x1", "x2")` |
| `tl_plot_nn_architecture()` | Neural network structure | `tl_plot_nn_architecture(model)` |

## Model Comparison & Selection

| Function | Description | Example |
|----------|-------------|---------|
| `tl_plot_model_comparison()` | Compare model performance | `tl_plot_model_comparison(model1, model2, test_data)` |
| `tl_plot_importance_comparison()` | Compare feature importance | `tl_plot_importance_comparison(model1, model2)` |
| `tl_find_optimal_threshold()` | Find optimal threshold | `tl_find_optimal_threshold(model, optimize_for = "f1")` |
| `tl_tune_nn()` | Tune neural network | `tl_tune_nn(data, formula, sizes = c(5, 10))` |
| `tl_tune_deep()` | Tune deep learning model | `tl_tune_deep(data, formula)` |
| `tl_plot_regularization_path()` | Visualize regularization | `tl_plot_regularization_path(model)` |
| `tl_plot_cv_results()` | Visualize CV results | `tl_plot_cv_results(cv_results)` |

## Interactive Exploration

| Function | Description | Example |
|----------|-------------|---------|
| `tl_dashboard()` | Interactive model dashboard | `tl_dashboard(model, test_data)` |

## Prediction Types

| Type | Description | Example |
|------|-------------|---------|
| `"response"` | Default predictions | `predict(model, new_data, type = "response")` |
| `"prob"` | Probability predictions | `predict(model, new_data, type = "prob")` |
| `"class"` | Class predictions | `predict(model, new_data, type = "class")` |

## Common Workflows

### Basic Workflow
```{r}
# Train model
model <- tl_model(train_data, y ~ ., method = "forest")

# Evaluate
tl_evaluate(model, test_data)

# Visualize
tl_plot_importance(model)

# Predict
predictions <- predict(model, new_data)
```

### Model Selection Workflow
```{r}
# Train several models
model1 <- tl_model(train_data, y ~ ., method = "linear")
model2 <- tl_model(train_data, y ~ ., method = "forest")
model3 <- tl_model(train_data, y ~ ., method = "boost")

# Compare performance
tl_plot_model_comparison(model1, model2, model3, 
                         test_data, 
                         names = c("Linear", "Forest", "Boost"))

# Compare importance
tl_plot_importance_comparison(model1, model2, model3)
```

### Cross-Validation Workflow
```{r}
# Perform cross-validation
cv_results <- tl_cv(data, y ~ ., method = "forest", folds = 5)

# Examine results
cv_results$summary

# Visualize
tl_plot_cv_results(cv_results)
```

## Data Preparation with Recipes

```{r}
# Create a recipe for preprocessing
library(recipes)
rec <- recipe(y ~ ., data = train_data) %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors()) %>%
  prep(training = train_data)

# Apply preprocessing
train_processed <- bake(rec, new_data = train_data)
test_processed <- bake(rec, new_data = test_data)

# Train model on processed data
model <- tl_model(train_processed, y ~ ., method = "forest")
```
