---
title: "Classification with tidysl"
author: "tidysl Team"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Classification with tidysl}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5
)
```

## Introduction

This vignette demonstrates how to use the `tidysl` package for classification tasks. The `tidysl` package provides a consistent interface for various supervised learning methods following tidyverse principles.

## Setup

First, let's load the necessary packages:

```{r packages, message=FALSE, warning=FALSE}
library(tidysl)
library(tidyverse)
library(modeldata)  # For example datasets
```

## Example Data

We'll use the Credit data for our classification example:

```{r data}
data(credit_data)
credit_df <- as_tibble(credit_data)

# Convert Status to a factor
credit_df$Status <- factor(credit_df$Status)

# Split into training and testing sets
set.seed(123)
train_indices <- sample(1:nrow(credit_df), 0.8 * nrow(credit_df))
train_data <- credit_df[train_indices, ]
test_data <- credit_df[-train_indices, ]

# Examine the data
glimpse(credit_df)
```

## Logistic Regression

Let's start with a logistic regression model:

```{r logistic}
# Fit a logistic regression model
log_model <- tl_model(
  data = train_data,
  formula = Status ~ .,
  method = "logistic"
)

# Print model summary
print(log_model)
summary(log_model)
```

## Model Evaluation

We can evaluate the model on test data:

```{r evaluation}
# Evaluate on test data
log_eval <- tl_evaluate(log_model, test_data)
log_eval
```

## Model Visualization

`tidysl` provides various visualization functions for classification:

```{r visualization}
# Plot ROC curve
tl_plot_roc(log_model, test_data)

# Plot confusion matrix
tl_plot_confusion(log_model, test_data)

# Plot precision-recall curve
tl_plot_precision_recall(log_model, test_data)

# Plot calibration curve
tl_plot_calibration(log_model, test_data)
```

## Finding the Optimal Threshold

For binary classification, we can find the optimal threshold:

```{r threshold}
# Find the optimal threshold for F1 score
threshold_results <- tl_find_optimal_threshold(
  log_model, 
  test_data, 
  optimize_for = "f1"
)

# Display results
threshold_results$optimal_threshold
threshold_results$optimal_value

# Plot threshold values
ggplot(threshold_results$all_thresholds, aes(x = threshold, y = value)) +
  geom_line() +
  geom_point() +
  geom_vline(xintercept = threshold_results$optimal_threshold, 
             linetype = "dashed", color = "red") +
  labs(title = "F1 Score by Threshold",
       x = "Threshold",
       y = "F1 Score") +
  theme_minimal()
```

## Regularized Logistic Regression

We can use regularization to improve performance:

```{r regularized}
# Fit a ridge-regularized logistic regression model
ridge_log_model <- tl_model(
  data = train_data,
  formula = Status ~ .,
  method = "ridge",
  is_classification = TRUE
)

# Evaluate on test data
ridge_log_eval <- tl_evaluate(ridge_log_model, test_data)
ridge_log_eval

# Plot regularization path
tl_plot_regularization_path(ridge_log_model)
```

## Decision Trees and Random Forests

Decision trees are popular for classification:

```{r trees}
# Fit a decision tree
tree_model <- tl_model(
  data = train_data,
  formula = Status ~ .,
  method = "tree",
  is_classification = TRUE,
  cp = 0.01
)

# Evaluate on test data
tree_eval <- tl_evaluate(tree_model, test_data)
tree_eval

# Plot the decision tree
if (requireNamespace("rpart.plot", quietly = TRUE)) {
  tl_plot_tree(tree_model)
}

# Fit a random forest
forest_model <- tl_model(
  data = train_data,
  formula = Status ~ .,
  method = "forest",
  is_classification = TRUE,
  ntree = 100
)

# Evaluate on test data
forest_eval <- tl_evaluate(forest_model, test_data)
forest_eval

# Plot feature importance
tl_plot_importance(forest_model)
```

## Gradient Boosting

Gradient boosting often achieves great performance:

```{r boosting}
# Fit a gradient boosting model
boost_model <- tl_model(
  data = train_data,
  formula = Status ~ .,
  method = "boost",
  is_classification = TRUE,
  n.trees = 100,
  interaction.depth = 3,
  shrinkage = 0.1
)

# Evaluate on test data
boost_eval <- tl_evaluate(boost_model, test_data)
boost_eval

# Plot feature importance
tl_plot_importance(boost_model)

# Partial dependence plot for an important feature
tl_plot_partial_dependence(boost_model, "Age")
```

## Support Vector Machines

SVMs can be effective for classification:

```{r svm}
# Fit an SVM model
svm_model <- tl_model(
  data = train_data,
  formula = Status ~ .,
  method = "svm",
  is_classification = TRUE,
  kernel = "radial",
  probability = TRUE
)

# Evaluate on test data
svm_eval <- tl_evaluate(svm_model, test_data)
svm_eval

# Plot decision boundary for two features
if (requireNamespace("e1071", quietly = TRUE)) {
  tl_plot_svm_boundary(svm_model, "Income", "Price")
}
```

## Cross-Validation

We can use cross-validation to assess model performance:

```{r cv}
# Perform cross-validation for logistic model
log_cv <- tl_cv(
  data = train_data,
  formula = Status ~ .,
  method = "logistic",
  folds = 5
)

# Examine CV results
log_cv$summary

# Plot CV results
tl_plot_cv_results(log_cv)
```

## Advanced Evaluation Metrics

`tidysl` provides additional evaluation plots for classification:

```{r advanced-metrics}
# Lift chart
tl_plot_lift(forest_model, test_data)

# Gain chart
tl_plot_gain(forest_model, test_data)
```

## Model Comparison

We can compare the performance of different models:

```{r comparison}
# Compare models
tl_plot_model_comparison(
  log_model, ridge_log_model, tree_model, forest_model, boost_model, svm_model,
  new_data = test_data,
  names = c("Logistic", "Ridge", "Tree", "Random Forest", "Boost", "SVM")
)

# Compare feature importance
tl_plot_importance_comparison(
  tree_model, forest_model, boost_model,
  names = c("Tree", "Random Forest", "Boost")
)
```

## Neural Networks

For complex relationships, we can use neural networks:

```{r neural-networks}
# Check if nnet is available
if (requireNamespace("nnet", quietly = TRUE)) {
  # Fit a neural network
  nn_model <- tl_model(
    data = train_data,
    formula = Status ~ .,
    method = "nn",
    is_classification = TRUE,
    size = 5,
    decay = 0.1
  )
  
  # Evaluate on test data
  nn_eval <- tl_evaluate(nn_model, test_data)
  nn_eval
  
  # Plot neural network architecture if NeuralNetTools is available
  if (requireNamespace("NeuralNetTools", quietly = TRUE)) {
    tl_plot_nn_architecture(nn_model)
  }
}
```

## Model Dashboard

`tidysl` provides an interactive dashboard for exploring model performance:

```{r dashboard, eval=FALSE}
# Launch dashboard (only run interactively)
if (requireNamespace("shiny", quietly = TRUE) && 
    requireNamespace("shinydashboard", quietly = TRUE) && 
    requireNamespace("DT", quietly = TRUE)) {
  tl_dashboard(forest_model, test_data)
}
```

## Conclusion

This vignette demonstrated how to use the `tidysl` package for classification tasks. The package provides a consistent interface for various supervised learning methods, making it easy to try different approaches and compare their performance.

Key features:
- Simple, consistent API across different models
- Integration with the tidyverse
- Comprehensive evaluation metrics
- Informative visualizations
- Support for model comparison

In the regression vignette, we explored how to use the package for regression tasks.
